E Coli Project Paper Incredibly Rough Draft

### 2013-09-01 paper/paper.tex
added writing to paper, although most of it is in note form, Im adding a lot of references Tested everything on crystal.

>>>>

A significant amount of work has been done in simulating and studying
the dynamics of the Min protein system and cells. A number of
different models have been simulated and studied.  They divide into
two natural groups - stochastic (specific protein positions are
tracked at all times) and deterministic (protein averages are used
along with rate constants to simulate interaction). They also split up
into other groups - cooperative attachement (MinD on the cytoplasm is
attracted to other MinD on cytoplasm, shown by non-linear attachement
on walls experimentally).  Huangs' 2003 and Meinhardt and De Boer 2001
are of this type.  Huang's seuccessfully predicts that breakdown of
striped oscillation pattern occurs when exchange of ATP for ADP bound
to cytosolic MinD is not too fast.  There is as well aggregation
current models, characterized by the proteins moving along the
membranes in a way so that they're attracted to other proteins on the
walls.  We are simulating Huang's model, so a further test of the
robustness of the oscillations with wild type values, and as well
compare against exprimental evidence given by mannik.  We use Huang's
becuase of the success so far, and then also the other type
(aggregation current models) depend on there being limited binding
spots on the membrane for minD.  This author also states that the
deterministic models have largely varified stochastic model
results.\cite{kruse2007experimentalist}

\cite{howard2005cellular}\cite{kruse2002dynamic}

Huang has also made simulation studies of round cell shapes and shown
that oscillations occur in these cell shapes, and that their behavior
depends on the radius of the shape. They show that the Min proteins can
select the long axis of the nearly round shapes based soley on the
geometry of the cell.\cite{huang2004min} \fixme{definately want to get
  this paper and read it}

Previous experimental studies have shown that MinC, known to inhibit
the FtZ polymer, exhibits an oscilatory, pole to pole behavoir in conjunction with
MinD and MinE. \cite{hu1999topological}

The function of the Min system might not be restricted to proper cell
division.  There is evidence that it is instrumental in the
dissasembly of the cytokinetic ring directly after cell division,
insuring that cell division takes place only once per cell
cycle. \cite{van2010mincdj}

Other simulations have been shown to exhibit oscillations in the
cylinder shaped cell.  While Huangs' 2003 study involves stages of
protein compounds (attached proteins), the differential equations
governing protein mobility in this study are designed with free
unattached proteins who interact with eachother.  Huang does cite this
paper so we can say that he followed and improved upon these
simulations.\cite{meinhardt2001pattern}

The MinE has been observed in the center of the cell and it's ability
to counteract what's refered to as MinCD cell division inhibitor has
been known.  It's been found that its not stationary but undergoes
repetitive movement back and forth. \cite{fu2001mine}

Previous studies have been made of the Min system's associtation with
the cell membrane
\cite{hsieh2010direct}\cite{mileykovskaya2003effects}. Previous
studies have shown that phospho lipids on the cell wall attract
MinD/MinE proteins and reduce ATPase activity.  It's further been
shown that the proteins interact preferebly with anionic lipids that
are localized at the poles of the cell.\cite{renner2012mind}

Expreiemntal studies have been made of the process of septum formation
in the middle of the pill shaped cell and its effect on MinD
oscillations, leading to the conclusion that it is geometry of septum
formation that allows for the creation of two MinD oscillation systems, one
in each daughter cell. \cite{juarez2010changes}
